% !TEX root = ../main.tex
\clearemptydoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgements}

\vspace*{2cm}

\begin{center}
{\Large \textbf{Acknowledgments}}
\end{center}

\vspace{1cm}

% \begin{center}
% I would like to thank Christian and Arno for their support and guidance throughout the 
% As I sit down to pen the acknowledgments for this thesis, I find myself reflecting on the journey that has been; a journey paved with challenges, learning, and immense support from a constellation of remarkable individuals. It is with a heart brimming with gratitude that I take this moment to extend my deepest thanks to each one of them.
I offer my deepest gratitude to my supervisors Christian Gscheidle and Arno Feiden. Since introducing and entrusting me with this intriguing research topic, your belief in my potential was a beacon that lit my way. No query, however trivial, went unanswered, as you stood by me every step of the way. Your availability and patience have been a source of immense encouragement, making this journey smoother and more meaningful. Your commitment to our weekly Tuesday check-ins and your deeply involved participation in our discussions consistently motivated me to push myself further and reach new heights. \\

I am profoundly grateful to Prof. Dr. Jochen Garcke for providing me with the opportunity to pursue my research at Fraunhofer SCAI and for being a pivotal figure during in this journey. His critical insights came at a crucial juncture of my research and his feedback was transformative, providing clarity and direction when most needed. \\

The resources and infrastructure provided by Fraunhofer-Gesellschaft's Scientific Computing and Algorithms (SCAI) institute, including access to the High-Performance Computing cluster and the suite of software, have been indispensable in the successful completion of my project, and I am deeply appreciative of it. \\

I extend my gratitude to Kislaya Ravi, whose role as a supervisor at the university extended far beyond traditional oversight. His willingness to lend an ear and offer timely advice proved invaluable in this endeavor. \\

I also wish to express my appreciation to my friends, whose belief in me remained steadfast during moments of doubt and despair. Their encouragement, laughter, and solace through all the phases of this journey were invaluable in keeping my spirits high.\\

To my parents, Amma and Appa, I owe an immeasurable debt of gratitude for your unconditional love and unwavering support, which have been the cornerstone of my perseverance and success. Your constant encouragement and belief in me have been my greatest source of motivation. Thank you for everything. \\

% To all the people who have a part of this journey, your support has made all the difference. Thank you. \\

\end{center}
